% THEORETICAL FRAMEWORK

\cleardoublepage

\chapter{Theoretical framework}
\label{theoretical-framework}

\section{Problem Definition}
\label{problem-definition}
The problem of image registration is defined as... (insert equation)

\section{Displacement Fields}
\label{displacement-fields}

\section{Diffeomorphism}
\label{Diffeomorphism}

\section{Classical Methods}
\label{classical-methods}
Demons, other iterative methods...

\section{Deep learning-based methods}
\label{deep-learning-methods}
When approaching the original problem of image registration... When using deep learning, we don't directly calculate the 


Differences between unsupervised and supervised deep learning methods.

\subsection{U-Net}
\label{u-net}
Some paper of implementation using U-Net or similar model

\section{Transformers}
\label{transformers}
Transformers were introduced ...

Currently, state of the art in sequence processing, tasks such as NLP...

\subsection{Mechanism of Self-attention}
\label{self-attention}

When using transformers, the input sequence is tokenized, obtaining a set of tokens - a collection of distinct, unordeded elements.


The next step is the projection of the tokens into a distributed geometrical space of continuous-valued vectors - what is referred to as an embedding. This is done in order to preserve the semantical relationships among the tokens.
In this low-dimensional space, we expect that the projections of the original tokens which hold stronger semantic relationships with each other are, indeed, closer to each other than their counterparts.


However, after the tokenization step, we have effectively lost the order of the original sequence. In order to maintain the notion of order necessary to process the input as a sequence,
transformer blocks use positional encoding.

Positional encoding alters the embeddings depending of the position of the token in the original sequence.

One of the possible techniques for implementing positional encoding is using the sinousoidal function. 

We then perform feature-based attention on the resulting embeddings.
The inductive bias by which feature-based attention is based upon, is to allow the network to place its attention not only based
in the original order of the sequence, but taking into account the content of the tokens.

In order to quantify the similarity of tokens, we will calculate the vector similarity among the tokens' projections
into the learned embedding space. As this is a low-dimensional space, we can make use of the inner vector product.

The transformer uses 3 different representations of the embedding matrix, the queries, keys and values.

For each token (i.e. vector), we create a query vector, key vector and value vector. The query, key and value matrices are
learned as part of the training process.
In order to reduce the computational complexity of the operation, this resulting vectors are usually in lower-dimensional spaces.

The concepts of key, value and query are originally part of information retrieval systems.


Self attention is performed for each position.

The main idea is that we compute the similarity of each token of the sequence with each other token. Then, the result of the 
self-attention is a vector, result of the sum of each token in the sequence multiplied by its similarity score. In this
way, we are capturing the most important context individually for each of the tokens in the sequence.


Self-attention with matrices
First, we obtain the query, key and value matrices by multiplying the embedding matrix with the learned weight matrices WQ, WK, WV.
Each of the rows of the embedding matrix corresponds to a token of the input sequence.

$$softmax(\frac{Q x K^T}{\sqrt{d_k}}) V = Z$$

The softmax outputs a probability distribution, with all of its components adding to one.

This concept of self-attention is further developed with multi-headed attention.

\subsection{Multi-head Self-attention}
\label{multihead-self-attention}

With multi-headed attention, we repeat the original self-attention process, obtaining multiple representational spaces, in the form of 
multiple sets of query, key and value matrices. Theoretically, this allows the model to perform attention in different, independent low-dimensional spaces, which
translates to the ability to jointly perform attention from different representation subspaces, at different positions.

\section{Visual transformers}
\label{visual-transformers}

